\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}} 
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\ 
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino
\begin{document}
\headerfontiii

%==================== HEADER ====================
\begin{center}
    {\Huge \textbf{JiaYang (Rocky) Wu}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    Champaign, IL \quad|\quad +1 (217) 328-6609 \quad|\quad
    \href{mailto:jywu3@illinois.edu}{jywu3@illinois.edu} \quad|\quad
    \href{mailto:rockyforwork123@gmail.com}{rockyforwork123@gmail.com} \quad|\quad
    \href{https://linkedin.com/in/jiayang-wu-85b960179}{linkedin.com/in/jiayang-wu-85b960179}
    }
\end{center}

\vspace{-4mm}

%==================== EDUCATION ====================
\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{University of Illinois at Urbana-Champaign}{Champaign, IL}
{Bachelor of Science in Information Science \& Data Science (Minor: Computer Science)}{Aug 2020 - May 2024}
\resumeItemListStart
    \item GPA: 3.58 
    \item Relevant Coursework: Data Analytics, Data Structures, Database Concepts, Machine Learning, Deep Learning
\resumeItemListEnd

\resumeSubheading
{University of Illinois at Urbana-Champaign}{Champaign, IL}
{Master of Science in Information Management (Minor: Computer Science)}{Aug 2024 - Dec 2025}
\resumeItemListStart
    \item Focus on Data Analytics, Cloud Computing, and Financial Data Management
\resumeItemListEnd

\resumeSubHeadingListEnd

%==================== EXPERIENCE ====================
\section{\textbf{Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

%ActionTec Electronics
\resumeSubheading
{ActionTec Electronics Co., LTD}{Hybrid, Santa Clara}
{Data Analyst and Model Building Intern}
{August 2025 - December 2025}
\resumeItemListStart
    \item Developed the second version of the \textbf{User Experience Quality (QoE) Wi-Fi Health Score System}, refactoring the original architecture to support \textbf{cloud deployment} and concurrent processing across multiple devices.
    \item Designed and implemented a \textbf{cloud-based data processing pipeline}: migrated local Shell scripts to AWS Docker EC2 container services with Athena, upgrading the architecture from single-point Linux access point testing to \textbf{data center-level distributed analysis}.
    \item Constructed an \textbf{end-to-end data pipeline}: Developed automated data collection and upload modules using Python, combined with SQL-optimized processing logic to support \textbf{real-time analysis} requirements
    \item Iteratively optimized scoring algorithms and developed a \textbf{real-time monitoring dashboard}, integrating interactive visualizations to boost Wi-Fi network health assessment efficiency by \textbf{60\%}
    \item Authored a comprehensive \textbf{technical documentation system} (covering code repository architecture, data collection protocols, and model logic specifications), laying the foundation for future AI model integration and system optimization

Translated with DeepL.com (free version)
\resumeItemListEnd
%ActionTec Electronics
\resumeSubheading
{ActionTec Electronics Co., LTD}{Hybrid, Santa Clara}
{Data Analyst and Model Building Intern}
{May 2025 - August 2025}
\resumeItemListStart
    \item Developed a comprehensive Quality of Experience (QoE) Wi-Fi Health Score system to quantify and analyze Wi-Fi access point performance across seven distinct metric categories.
    \item Engineered and enhanced a data-gathering shell script through 27 iterations, evolving it from a basic data collector to a sophisticated tool for detailed coverage analysis on Linux-based access points.
    \item Utilized Python to conduct in-depth data analysis, cleaning, and visualization, successfully developing and validating robust statistical models for key performance metrics like speed and coverage.
    \item Innovated the metric calculation process to be more user-centric, transforming raw speed into "Performance Potential" and redesigning the coverage score to better reflect user experience.
    \item Experimented with and applied statistical algorithms, including ANOVA and PCA, to develop a holistic model that combines multiple metrics into a single, actionable health score.
    \item Identified key areas for user experience improvement, proposing actionable solutions such as contextual dashboards and a prioritization model to make the health score more intuitive for end-users.
    \item Authored comprehensive documentation for the codebase, data-gathering procedures, and model logic to ensure a seamless handover and facilitate future development.
\resumeItemListEnd

% AIFINSPHERE
\resumeSubheading
{AiFinSphere Co., LTD – AI Quantitative Hedge Fund}{Remote, Champaign}
{Data Analyst and Model Building Intern}{August 2024 – October 2024}
\resumeItemListStart
  \item Implemented a \textbf{Black-Scholes Model} integrating Interactive Brokers' Trader Workstation API, implementing implied volatility calculations via \textbf{Newton-Raphson} method for simulated trading operations in Python.
  \item Analyzed market prices and temporal data, leveraging Spark-based data warehousing of high-volume technology stocks (AMD, NVIDIA) to expedite parallel data processing.
  \item Orchestrated the ingestion and unification of hundreds of millions of transaction records (ETFs, stocks, and profit metrics), elevating modeling accuracy and improving computational efficiency by 10\%.
  \item \textbf{Tax and Accounting Project Extension}: Emulated a \textit{broker environment} to calculate potential \textbf{tax liabilities} arising from complex portfolio trading activities; generated reconciliation reports documenting trades, gains/losses, and corresponding tax considerations.
  \item Employed \textbf{Generative AI tools} (ChatGPT, Claude) for adaptive learning, refining approach to quant strategies, ensuring thorough comprehension of portfolio risk analytics, and clarifying supervisor requirements.
\resumeItemListEnd

% SDIC
\resumeSubheading
{SDIC Securities Co., LTD – Leading Securities Company}{Shanghai, China}
{Data Analyst and Software Development Engineer Intern}{June 2024 – August 2024}
\resumeItemListStart
  \item Built a multiprocessing Python pipeline that consolidates data from MySQL and Oracle to form a baseline for \textbf{quantitative model building} and visualization.
  \item Integrated massive cross-asset datasets (ETFs, stocks, profit data) and generated visual dashboards (pie charts, bar graphs) focusing on profit distributions, transaction frequency by date, and average transaction amounts in positive vs. reverse trades.
  \item Enhanced program performance by 15\% through \textbf{multiprocessing, error handling queues}, and well-structured helper functions.
  \item \textbf{Leveraged Generative AI} (ChatGPT) to automate code QA and query optimization, improving data manipulation speed and clarifying advanced SQL operations.
\resumeItemListEnd

% ACTIONTEC
\resumeSubheading
{Actiontec Co. Ltd – Leading Broadband Access Provider}{Santa Clara, CA}
{Data Analyst Intern, Data \& Analytics}{December 2023 – May 2024}
\resumeItemListStart
  \item Developed a \textbf{data model} integrating multi-source data (S3 Parquet, MySQL on AWS) and leveraged Athena Query for foundational \textbf{ML evaluations}.
  \item Consolidated and manipulated over \textbf{1 million records} of product alarm data, enabling the dev team to pinpoint and debug Wi-Fi modem issues.
  \item Created a comprehensive \textbf{data dictionary} detailing data flows, definitions, and integrity rules, supporting robust cleansing practices.
  \item Used \textbf{ChatGPT and Claude} to enhance understanding of analytics project scope, quickly research best practices for data dictionary creation, and confirm alignment with supervisor's requirements.
\resumeItemListEnd

% TENCENT
\resumeSubheading
{TENCENT Co. Ltd – Global Tech Giant}{Shenzhen, China}
{Data Analyst Intern, Big Data Brain}{June 2023 – August 2023}
\resumeItemListStart
  \item Architected an SQL pipeline that automates query generation from human-language prompts with \textbf{80\% accuracy} in bridging semantic to SQL keyword mapping.
  \item Managed \textbf{data extraction and cleaning} for large-scale text inputs, addressing missing values, outlier checks, and complex NLP transformations.
  \item Created and refined \textbf{100+ MySQL test cases} for an NLP deep learning model, boosting \textbf{training/validation efficiency by 20\%}.
  \item Developed a Python-based database migration utility with advanced JSON parsing for seamless data integration.
  \item Adopted \textbf{generative AI} to explore advanced NLP/ML frameworks (e.g., prompt-tuning strategies) and accelerate the test-case generation process.
\resumeItemListEnd

% FEISU
\resumeSubheading
{FEISU TECHNOLOGY Co. Ltd – Startup in Shenzhen}{Shenzhen, China}
{Data Analyst Intern, Investment \& Marketing}{June 2021 – August 2021}
\resumeItemListStart
  \item Created a dynamic user-interface website using \textbf{Python, Django, MySQL} to analyze bi-annual sales data for Android apps (advertising spend, downloads, site visits, user subscriptions, ROI).
  \item Strengthened data integrity with \textbf{rigorous cleansing/validation} processes, ensuring reliability for data-driven product marketing.
  \item Identified trends and patterns through \textbf{comprehensive data analysis}, boosting advertisement ROI by 30\% within the app ecosystem.
  
\resumeItemListEnd

\resumeSubHeadingListEnd

%==================== PROJECTS (OPTIONAL) ====================
\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {Tax and Portfolio Reconciliation System (Independent Project)} 
  {Tools: Python, Pandas, Interactive Brokers API, ChatGPT/Claude}
  {October 2024 - Ongoing}
  {}
\resumeItemListStart
  \item Extended the AiFinSphere internship's scope to \textbf{simulate broker operations}, performing trades and automatically calculating tax liabilities, capital gains, and wash-sale implications.
  \item \textbf{Reconciled} transaction data with real-time market data, generating daily statements for trade P\&L and associated tax entries.
  \item Used \textbf{Generative AI} (ChatGPT, Claude) to swiftly interpret intricate US tax guidelines and confirm alignment with standard accounting practices.
  \item Produced comprehensive documentation detailing data processing logic, focusing on \textbf{tax considerations and compliance} best practices.
\resumeItemListEnd

\resumeSubHeadingListEnd

%==================== SKILLS ====================
\section{\textbf{Skills}}
\vspace{-0.4mm}
\resumeHeadingSkillStart
  \resumeSubItem{Programming Languages:}
    {Python, MySQL, C++, Java}
  \resumeSubItem{Data Analytics \& Machine Learning Tools:}
    {Spark, NumPy, Pandas, Tableau, Power BI, Alteryx, PyTorch, TensorFlow, Scikit-learn}
  \resumeSubItem{Database Systems:}
    {MySQL, AWS Athena}
  \resumeSubItem{Tax/Accounting:}
    {Basic US Tax Concepts (Capital Gains, Wash-Sale), Accounting Principles, Reconciliation}
  \resumeSubItem{Generative AI:}
    {ChatGPT, Claude (prompt engineering, adaptive learning for code/process improvement)}
  \resumeSubItem{Cloud/DevOps:}
    {AWS (EC2, S3), Docker, Git}
  \resumeSubItem{Other Skills:}
    {Parallel Processing, Statistical Modeling, ETL Pipelines, Data Warehousing, NLP}
\resumeHeadingSkillEnd

%==================== HONORS & AWARDS (OPTIONAL) ====================
%\section{\textbf{Honors and Awards}}
%\vspace{-0.4mm}
%\resumeSubHeadingListStart
%\resumeProject
%  {Award Name A}
%  {Awarding Institution/Organization}
%  {Month Year}
%  {{}[\href{https://award-link-a.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
%\resumeItemListStart
%  \item Brief description of the award and its significance
%  \item Impact or recognition associated with the award
%\resumeItemListEnd

%\resumeSubHeadingListEnd

%==================== ADDITIONAL INFORMATION ====================
\section{\textbf{Additional Information}}
\vspace{-0.4mm}
\small{
\textbf{Languages:} English (Fluent), Chinese (Native)

\textbf{Interests:} Finance, AI-powered Trading, Tax Policy, Machine Learning Research
}

%==================== REFERENCES (OPTIONAL) ====================
%\section{\textbf{References}}
%\vspace{-0.2mm}
%\small{
%\begin{enumerate}[leftmargin=*,labelsep=2mm]
%\item \textbf{Reference Person 1}\\
%   Job Title, Department\\
%   Organization Name\\
%   Email: email1@example.com\\
%   Phone: +X-XXX-XXX-XXXX\\
%   \textit{Relationship: [e.g., Thesis Advisor, Manager, etc.]}
%\end{enumerate}
%}

\end{document}